Describe and Explore: Using feature-based time series clustering to identify meaningful structures in intensive longitudinal data

### 2022-12-28 methods-and-results.Rmd
:art: figure placement

@@

>>>>

\begin{figure}[!ht] %hbtp
  \caption{Cluster Group Comparisons based on Features and Variables}
  \label{fig:clusterFeatVar}
  \centering\includegraphics[width=\textwidth]{figures/clusterFeatVarComb.pdf}
  \caption*{Note: \\
  Within the "(B) Feature Focus" subplot, the 'n' and 'Discrimination' comparison variables were not part of the original time series clustering.}
\end{figure}

@@

\begin{figure}[!ht] %hbtp
  \caption{Cluster Group Comparisons over time}
  \label{fig:clusterTs}
  \centering\includegraphics[width=\textwidth]{figures/clusterTsComb.pdf}
  \caption*{Note: \\
  Subplot (A) displays the variable cluster means at every measurement occasion. Subplot (B) shows the GAM spline for each cluster across the measurement occasions.}
\end{figure}
